\begin{enumerate}[label=\thechapter.\arabic*,ref=\thechapter.\theenumi]

\item Consider a unity-gain negative feedback system consisting of the plant $G\brak{s}$  and a proportional-integral controller. Let the proportional gain and integral
gain be 3 and 1, respectively. For a unit step reference input, the final values of the
controller output and the plant output, respectively, are
\begin{align}
    G\brak{s} = \frac{1}{\brak{s-1}} \notag
\end{align}\hfill (GATE EE 2023)\\
\solution 
\input{2023/EE/14/main.tex}
\newpage

\item Level \brak{h} in a steam boiler is controlled by manipulating the flow rate \brak{F} of the break-up(fresh) water using a proportional \brak{P} controller. The transfer function between the output and the manipulated input is   \\
$$ \frac{h\brak{s}}{F\brak{s}}=\frac{0.25\brak{1-s}}{s\brak{2s+1}} $$   \\
The measurement and the valve transfer functions are both equal to 1. A process engineer wants to tune the controller so that the closed loop response gives the decaying oscillations under the servo mode. Which one of the following is the CORRECT value of the controller gain to be used by the engineer? \\
\begin{enumerate}[label=(\alph*)]
    \item $0.25$
    \item $2$
    \item $4$
    \item $6$
\end{enumerate} \hfill{GATE CH 2023} \\

\solution
\newpage
\item \input{2023/ME/30/me30.tex}

\item A system has transfer function
 \[\frac{Y(s)}{X(s)}=\frac {s-\pi}{s+\pi}\]
 let $u(t)$ be the unit step function.The input $x(t)$ that results in a steady-state output $y(t)=sin(\pi t)$ is \underline{\quad}.\hfill (GATE IN 2023)\\
 \solution
 \newpage
 \item The state equation of a second order system is \\
$ \dot{\bm{x}}(t) = A\bm{x}(t)$, \quad $\bm{x}(0)$ is the initial condition. \\
Suppose $\lambda_1$ and $\lambda_2$ are two distinct eigenvalues of $A$, and $\nu_1$ and $\nu_2$ are the corresponding eigenvectors. For constants $\alpha_1$ and $\alpha_2$, the solution, $\bm{x}(t)$, of the state equation is \\
\begin{enumerate}[label=(\Alph*)]
\item $\sum_{i=1}^{2} \alpha_ie^{\lambda_it}\bf{\nu}_i$
\item $\sum_{i=1}^{2} \alpha_ie^{2\lambda_it}\bf{\nu}_i$
\item $\sum_{i=1}^{2} \alpha_ie^{3\lambda_it}\bf{\nu}_i$
\item $\sum_{i=1}^{2} \alpha_ie^{4\lambda_it}\bf{\nu}_i$
\end{enumerate}
\hfill{GATE 2023 EC Question 43} \\
\newpage
\item Consider the complex function
\[ f(z) = \frac{z^{2}\sin z}{(z-\pi)^4} \]
At \( z = \pi \), which of the following options is (are) correct?
\begin{enumerate}[label=\textbf{\arabic*.}, font=\bfseries, align=left]
    \item[(A)] The order of the pole is 4 
    \item[(B)] The order of the pole is 3 
    \item[(C)] The residue at the pole is \( \frac{\pi}{6} \)
    \item[(D)] The residue at the pole is \( \frac{2\pi}{3} \)
\end{enumerate}
\hfill (GATE PH 2023)
\newpage
 \item
 A buoy of virtual mass $30$ kg oscillates in a fluid medium as a single degree of
freedom system. If the total damping in the system is set as $188.5$ N-s/m, such
that the oscillation just ceases to occur, then the natural period of the system is
\rule{1cm}{0.15mm} s (round off to one decimal place)
\hfill(GATE MN 2023 question 63)\\

\item The outlet concentration $C_A$ of a plug flow reactor (PFR) is controlled by manipulating the inlet concentration $C_{A0}$.The following transfer function describes the dynamics of this PFR.
\begin{align*}
    \frac{C_{A}(s)}{C_{A0}(s)}=e^{-(\frac{V}{F})(k+s)}
\end{align*}
In the above question, V=1$m^3$,F=0.1$m^3$$min^{-1}$ and k=0.5$min^{-1}$.The measurement and valve transfer functions are both equal to 1.The ultimate gain, defined as the proportional controller gain that produces sustained oscillations, for this system is\\ \hfill{(GATE 2023 CH 61)}\\
\solution
\end{enumerate}
